R Notebook

### 2021-12-01 Figures/Supp_figures.Rmd
update of supp figures
text size and description

for (i in 1:(ncol(data) - 1)) {
  cd4[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD4.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# CD8
cd8 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("CD8", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$T.cells.CD8)
for (i in 1:(ncol(data) - 1)) {
  cd8[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(CD8.*)|(_T_cell.*)|(_T.cell.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# Monocytes
mono <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("Mono", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Monocytes)
for (i in 1:(ncol(data) - 1)) {
  mono[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Mono.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = mono, ncol = 3, top = textGrob("Monocytes", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# M1
m1 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("M1", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Macrophages.M1)
for (i in 1:(ncol(data) - 1)) {
  m1[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(M1)|(_Macro.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = m1, ncol = 3, top = textGrob("Macrophages M1", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# M2
m2 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("(_M2)|(\\.M2)", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Macrophages.M2)
for (i in 1:(ncol(data) - 1)) {
  m2[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(M2)|(_Macro.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = m2, ncol = 3, top = textGrob("Macrophages M2", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# B
b <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("(B_cell)|(B.cell)|(B_lin)", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$B.cells)
for (i in 1:(ncol(data) - 1)) {
  b[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_(B_cell.*)|(_B.cell.*)|(_B_lin.*)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# NK
nk <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("NK", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$NK.cells)
for (i in 1:(ncol(data) - 1)) {
  nk[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_NK.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))

# neutro
neutro <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("Neu", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Neutrophils)
for (i in 1:(ncol(data) -1)) {
  neutro[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("") + xlab("") + ggtitle(str_remove_all(names(data)[i], "_Neu.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 6) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 6)
  })
}
grid.arrange(grobs = neutro, ncol = 3, top = textGrob("Neutrophils", gp=gpar(fontsize=20,font=3,face="bold")), left = textGrob("Deconvolution", gp=gpar(fontsize=14, face="bold"), rot=90), bottom= textGrob("FACS", gp=gpar(fontsize=14, face="bold")))
```

>>>>

for (i in 1:(ncol(data) - 1)) {
  cd4[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(T_cell.)|(T.cell.)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = cd4, ncol = 3, top = textGrob("CD4", gp=gpar(fontsize=20,font=3,face="bold")))

# CD8
cd8 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("CD8", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$T.cells.CD8)
for (i in 1:(ncol(data) - 1)) {
  cd8[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(T_cell.)|(T.cell.)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = cd8, ncol = 3, top = textGrob("CD8", gp=gpar(fontsize=20,font=3,face="bold")))

# Monocytes
mono <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("Mono", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Monocytes)
for (i in 1:(ncol(data) - 1)) {
  mono[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = mono, ncol = 3, top = textGrob("Monocytes", gp=gpar(fontsize=20,font=3,face="bold")))

# M1
m1 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("M1", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Macrophages.M1)
for (i in 1:(ncol(data) - 1)) {
  m1[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(Macrophage.)|(Macrophages.)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = m1, ncol = 3, top = textGrob("Macrophages M1", gp=gpar(fontsize=20,font=3,face="bold")))

# M2
m2 <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("(_M2)|(\\.M2)", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Macrophages.M2)
for (i in 1:(ncol(data) - 1)) {
  m2[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], "(Macrophage.)|(Macrophages.)")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = m2, ncol = 3, top = textGrob("Macrophages M2", gp=gpar(fontsize=20,font=3,face="bold")))

# B
b <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("(B_cell)|(B.cell)|(B_lin)", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$B.cells)
for (i in 1:(ncol(data) - 1)) {
  b[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(str_remove_all(names(data)[i], ".cell.*")) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = b, ncol = 3, top = textGrob("B cells", gp=gpar(fontsize=20,font=3,face="bold")))

# NK
nk <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("NK", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$NK.cells)
for (i in 1:(ncol(data) - 1)) {
  nk[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = nk, ncol = 3, top = textGrob("Natural Killers", gp=gpar(fontsize=20,font=3,face="bold")))

# neutro
neutro <- list()
data <- silico1700_deconv %>% select(colnames(silico1700_deconv)[grepl("Neu", colnames(silico1700_deconv))])
data <- data %>% select(order(colnames(.)))
data <- cbind(data, silico1700_facs$Neutrophils)
for (i in 1:(ncol(data) -1)) {
  neutro[[i]] <- local({
    i <- i
    x = ggplot(data, aes(x = data[, ncol(data)], y = data[, i])) +
      geom_point() +
      stat_smooth(method = lm, size = 0.2, color = "black", se = FALSE, fullrange = T) +
      scale_x_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.0, 0.2)) +
      scale_y_continuous(limits = c(0, max(data[, i])), breaks = seq(0.0, 1.2, 0.2)) +
      theme(axis.title.x= element_text(size = 12, face="bold"), 
          axis.title.y= element_text(size = 12, face="bold") )  + 
      ylab("Deconv estimate") + xlab("FACS") + ggtitle(names(data)[i]) +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), plot.title = element_text(color = "black", size = 14, face = "bold.italic", hjust = 0.5, vjust = 1.5)) +
      annotate("text", x = -Inf, y = Inf, hjust=-0.5, vjust=1, label = paste("italic(r)==", round(cor.test(data[, i], data[, ncol(data)])$est, 2), "~','", "~italic(P)<", "2.2e-16"), parse = TRUE, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=-1, vjust=2, label = paste("RMSE =", round(sqrt(mean((data[, i] - data[, ncol(data)])^2, na.rm = T)), 2)), parse = F, size = 7) +
      annotate("text", x = -Inf, y = Inf, hjust=2, vjust=3, label = paste("n = ", nrow(data)), size = 7)
  })
}
grid.arrange(grobs = neutro, ncol = 3, top = textGrob("Neutrophils", gp=gpar(fontsize=20,font=3,face="bold")))
```
